# Element Values

## More on list

When we use `list()`, it is like we are making a list. There are two types of list.

-   non-labelled items
-   Labelled items

------------------------------------------------------------------------

Shopping list (non-labelled items)

1.  milk

2.  apple

3.  pork

Here 1, 2 and 3 are not their label. It simply represents the position of the item on the shopping list, which is like the position of element value in a list.

It is like

```{r}
list(
  "milk", 
  "apple", 
  "pork"
)
```

------------------------------------------------------------------------

My enrolled course list (labelled list)

-   Compulsory

    -   Principle of Economics,

    -   Calculus,

    -   Accounting

-   Selective

    -   Philosophy,

    -   Chinese Literature

It is like

```{r}
list(
  Compulsory = 
    c("Principle of Economics", 
      "Calculus", 
      "Accounting"),
  Selective = 
    c("Philosophy", 
      "Chinese Literature")
)
```

------------------------------------------------------------------------

When we make a list it can be nested, like a concert event:

-   name

    -   **Gianandrea Noseda conducts Schumann and Mendelssohn --- With Mikhail Pletnev**

-   time

    -   2021, Oct, 01

-   Program

    -   Robert Schumann, Piano Concerto in A Minor, Op. 54

    -   Felix Mendelssohn-Bartholdy, Symphony No. 4 in A Major, Op. 90, "Italian"

```{r}
list(
  name="Gianandrea Noseda conducts Schumann and Mendelssohn — With Mikhail Pletnev",
  time="2021, Oct, 01",
  program=list(
    "Robert Schumann, Piano Concerto in A Minor, Op. 54",
    "Felix Mendelssohn-Bartholdy, Symphony No. 4 in A Major, Op. 90, Italian"
  )
)
```

When there are several concerts, the list can look like

1.  

    -   name

    -   time

    -   program

2.  

    -   name

    -   time

    -   program

Here the numbers indicate the position of element value. As a list, it would be like:

```{r}
list(
  list(
    name="name1",
    time="time1",
    program=list(
      "music1",
      "music2"
    )
  ),
  list(
    name="name2",
    time="time2",
    program=list(
      "musicA",
      "musicB"
    )
  )
)
```

::: {.exercise}
How would you store the following lists:

1.  Shopping list: egg x 2 dozens, milk x 1L, vegetable x 2 kinds.
2.  Make a list of two courses your take this semester with course name, time, and place
:::

***

### JSON data

JSON (Javascript Object Notation) is the most common data format that transmit across internet.

```{r}
browseURL("https://data.gov.tw/dataset/6013")

```


```{r}
concerts <- jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)

```


## Retrieve multiple element values

`[x]` where `x` is either

-   a numeric atomic vector, such as `c(1,2,5)`; or

-   a character atomic vector with element names.

```{r JohnsFamily}
JohnsFamily <-
  list(
    name = "John", age = 35,
    spouse = list(name = "Mary", age = 32),
    children = list(
      list(name = "Bill", age = 5),
      list(name = "Jane", age = 3)
    )
  )
```

-   There are 4 element values inside `JohnsFamily` list.

```{r}
# checking how many element values
length(JohnsFamily)
# checking element names
names(JohnsFamily)
```

John's name and age

```{r}
JohnsFamily[c(1,2)]
JohnsFamily[c("name", "age")]
```

::: {.alert .alert-info}
When you want to retrieve multiple element values from an object, the resulting vector will be the same type as its source object.

-   Source object `JohnsFamily` is of **list** type.

the returned vector will also be of **list** type.
:::

------------------------------------------------------------------------

When retrieving one element value it is better to use `[[]]` (or `$` only for list) instead of `[]`.

John's age

```{r}
JohnsFamily[["age"]] # or JohnsFamily[[2]]
JohnsFamily["age"] # or JohnsFamily[2]
```

-   `JohnsFamily[["age"]]` indeed retrieves the element **value**.

-   `JohnsFamily["age"]` create a vector of the same type as `JohnsFamily` to store the retrieved element value.

::: {.alert .alert-info}
`[]` is designed to retrieve multiple element values. Its resulting vector will always follow the same type as the source object.
:::

## Replacement

`[[]]<-`, `[]<-`, `$ <-`

```{r}
JohnsFamilyCopy <- JohnsFamily

JohnsFamilyCopy[[1]] <- "Watson" 
JohnsFamilyCopy[[1]]
```

When replace multiple element values at once, you need to respect their source structure, especially the type:

-   element 1 and 2 are from a source of `list` with names `name` and `age`.

```{r}
JohnsFamilyCopy[c(1,2)] <- 
  list(name="Watson", age=37) 
JohnsFamilyCopy[c(1,2)]
```

::: {.alert .alert-info}
You can also use

-   `-> [[]]`, `-> []`, `-> $`

    ```{r}
    "Watson" -> JohnsFamilyCopy[[1]]
    ```

-   `[[]]=`, `[]=`, `$ =`

    ```{r}
    JohnsFamilyCopy[[1]] = "Watson"
    ```
:::

You can chain retrieval operators:

```{r}
JohnsFamilyCopy$spouse[["age"]]
JohnsFamilyCopy$children[[1]]$name
```

## Add element values

Adding an element value is like

> Retrieve a non-existent element value and bind a value with it

```{r example1}
example1 <- c("John", "Mary", "Bill")
example1[["person4"]] <- "Ken"
example1[c(7,8)] <- c("person7"="Jack", "Janem")
example1
```

```{r}
JohnsFamilyCopy2 <- JohnsFamily
# Add a new born 
JohnsFamilyCopy2$children[[3]] <- 
  list(name="Lisa", age=0) # $ is for list only
```

::: {.exercise}
How do you add the new born if you use `JohnsFamilyCopy3$children[3] <-`:

```{r eval=F}
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <-

```
:::

------------------------------------------------------------------------

Adding element values is commonly used to construct whole vector.

For example, we can directly construct the following whole vector

```{r}
height <- c("001"=177, "002"=183, "003"=173)
```

Or we can

```{r}
height <- numeric(0) # Declaration

height[["001"]] <- 177
height[c("002", "003")] <- c(183, 173)
```

-   The first step creates an empty vector with type **numeric** and bind that value to a name called `height`.

::: {.alert .alert-info}
When you bind a name with no value but its value type, it is called **declaration**.
:::

-   Declaration is necessary since without it there is no value to operate retrieval on -- even our goal is to add values.

------------------------------------------------------------------------

Declare-then-add method is extremely convenient for list construction since a lot of time we know how we want to retrieve the information later.

Suppose we want to construct a list that can retrieve a student's class schedule in the following way later:

```{r}
# Retrieve the 1st course in semester 1, school year 108
classSchedule$yr108$semester1[[1]] 
# Retrieve the course name of the the 1st course in semester 1, school year 108
classSchedule$yr108$semester[[1]]$name
# Retrieve the course credit of the the 1st course in semester 1, school year 108
classSchedule$yr108$semester[[1]]$credit
```

Suppose the course is "programming for data science" with 2 credits.

Direct construction

```{r}
classSchedule <- list(
  yr108 = list(
    semester1 = list(
      list(
        name="programming for data science",
        credit=2
      )
    )
  )
)
```

This requires strong familiarity with **nested** list usage In this case, we can declare an empty list and use add method to complete the list:

```{r}
classSchedule <- list()
```

-   Be careful it is not `list(0)`.

```{r}
# Retrieve the course name of the the 1st course in semester 1, school year 108
classSchedule$yr108$semester[[1]]$name <- "programming for data science"
# Retrieve the course credit of the the 1st course in semester 1, school year 108
classSchedule$yr108$semester[[1]]$credit <- 2
```

## Remove element values

> Retrieve element values you want and bind it with the source object again

-   `[- c(position_indices)]` will leave those you don't want and retrieve only those that you want.

```{r}
example2 <- c("John", "Mary", "Bill", person4="Jack")

example2[-c(4)] # retrieves what you want

example2 <- example2[-c(4)] # bind the retrieval of the wanted with the source object
```

::: {.alert .alert-warning}
`- c()` does **NOT** work with **element names**, so you cannot:

```{r}
example2 <- c("John", "Mary", "Bill", person4="Jack")
example2[-c("person4")]
```
:::

::: {.alert .alert-danger}
Operation `-c()` is designed for keeping **multiple** elements by excluding the unwanted, you always use `[]`:

```{r}
example2copy1 <- example2copy2 <- c("John", "Mary")

example2copy1[-c(2)] # Okay

exmaple2copy1[[-c(2)]] # Error
```
:::

::: {.exercise}
If John divorced Mary, how do you change the record by removing the spouse element?

```{r, eval=FALSE}
JohnsFamilyCopy4 <- JohnsFamily
```
:::

------------------------------------------------------------------------

list has an external removal technique, which is to bind **NULL** with the retrieved element value.

```{r}
JohnsFamilyCopy5 <- JohnsFamilyCopy6 <- JohnsFamilyCopy7 <- JohnsFamilyCopy8 <-  JohnsFamily
```

Techniques that apply to both atomic vector and list:

```{r}
JohnsFamilyCopy5 <- 
  JohnsFamilyCopy5[-c(3)]
```

Techniques that apply only to list

```{r}
JohnsFamilyCopy6$spouse <- NULL
```

Remove multiple elements at once:

```{r}
JohnsFamilyCopy7[c(3, 4)] <- NULL
```

::: {.alert .alert-danger}
When removing multiple elements on list, don't use:

```{r}
JohnsFamilyCopy8[c(3, 4)] <- list(NULL, NULL)
```

This will become **replacement**. Only replacement on multiple element values requires you to respect its source type.
:::
