
Exercise 3.2 From concerts_obo,

Retrieve the 3rd and 5th concert observations and bind the result value with an object name concerts_sampled.

For the second concert, what are its first show’s time and location? Retrieve the information and bind the value with firstShowInfo.

```{r}
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)
```

```{r}
firstShowInfo <- 
  concerts_obo[[2]]$showInfo[[1]][c("time","location")]
firstShowInfo # name call to show answer
```


Exercise 3.3 From concerts_obo, due to Covid-19 the 3rd concert’s 1st show time is changed to “2022/01/31 19:30:00” and the location is changed to “Taichung Opera House”, please change the information

```{r}
concerts_obo -> concerts_oboCopy
concerts_oboCopy[[3]]$showInfo[[1]]$time <- "2022/01/31 19:30:00"
concerts_oboCopy[[3]]$showInfo[[1]]$location <- "Taichung Opera House"

concerts_oboCopy[[3]]$showInfo[[1]][c("time", "location")] # name call to show answer
```

Exercise 3.4 How do you add the new born if you use JohnsFamilyCopy3$children[3] <-:

```{r}
JohnsFamily <-
  list(
    name = "John", 
    age = 35,
    spouse = list(
      name = "Mary", 
      age = 32),
    children = list(
      list(
        name = "Bill", 
        age = 5),
      list(
        name = "Jane", 
        age = 3)
    )
  )
```

```{r}
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <- 
  list(
    list(
      name="Lisa",
      age=0
    )
  )

JohnsFamilyCopy3$children[3] # name call to show answer
```


Exercise 3.5 The 5th concert decides to add one more show which shares the same show information as its first show except the date is 2 days later.

```{r}
concerts_obo -> concerts_oboCopy
# add one more show, and
# shares the same show information as its first show

# name call to retrieve a non-existent element value: concerts_oboCopy[[5]]$showInfo[[2]]
# give that name call retrieval the value you want use binding <- 
concerts_oboCopy[[5]]$showInfo[[2]] <- 
  concerts_oboCopy[[5]]$showInfo[[1]]

# except the date is 2 days later
#  modify new show's day information

# check wrong values to be corrected
concerts_oboCopy[[5]]$showInfo[[2]]$time 
concerts_oboCopy[[5]]$showInfo[[2]]$endTime  
# correct the values
concerts_oboCopy[[5]]$showInfo[[2]]$time <-
  "2022/05/16 10:00:00" 
concerts_oboCopy[[5]]$showInfo[[2]]$endTime <-
  "2022/05/17 22:00:00"

concerts_oboCopy[[5]]$showInfo[[2]] # name call to show answer
```

Exercise 3.6 Due to Covid-19 concerts 2, 5, 7 are cancelled. Remove those three concerts from concerts_obo.

```{r}
concerts_obo -> concerts_oboCopy
concerts_oboCopy[-c(2, 5, 7)] -> concerts_oboCopy
# Since concerts_obo is a list, you can also do
concerts_obo -> concerts_oboCopy
concerts_oboCopy[c(2,5,7)] <- NULL

```

