---
title: "Oct. 6"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

## Basic data type

Singleton


## Collection of values

### Atomic vector

```{r}
c("John", "Mary")
```

### list (vector)

```{r}
list()
list("John", 178, TRUE)
```

```{r}
typeof("John")
typeof(c("John", "Mary"))
typeof(list("John", 178, TRUE))
```

```{r}
list("John", 5, TRUE)
```

```{r}
list("John",42, list("Mary", 35)) # big list (a nested list)
```


element values of the above list:

```{r}
"John" 
42
"Mary" # is not an elment value of the list
35 # is not an element value of the list
```

```{r}
"John"
42
list("Mary", 35)
```

## 2.8

```{r}
c("John", "Mary")[[1]]
```


```{r}
c("John", "Mary")[[2]]
```

```{r}
list("John", 178, TRUE)[[1]] # "John"
list("John", 178, TRUE)[[2]] # 178
list("John", 178, TRUE)[[3]] # TRUE
```


```{r}
list("John",42, list("Mary", 35))
```

```{r}
"John" # 1
42 # 2
list("Mary", 35) #3
```


```{r}
list("John",42, list("Mary", 35))[[3]]
```

## 2.9

```{r}
personName = c("John", "Mary")
interestingNumber = c(2, 3.1412)
covidPositive = c(TRUE, TRUE, F)
```

```{r}
personName = c("John", "Mary") # binding
personName # call name
```

```{r}
personName = c("John", "Mary") 
personName <- c("John", "Mary") 
c("John", "Mary") -> personName
```

### Chained extraction operations

[[]]
[]
$

[,]

```{r}
bigList <- list("John",42, list("Mary", 35))
```


```{r}
bigList[[3]][[2]]
```
  
   * There is a call to bigList

```{r}
list("John",42, list("Mary", 35))[[3]][[2]]
```

   *
Resolve First
```{r}
list("John",42, list("Mary", 35))[[3]]
```

```{r}
list("Mary", 35)[[2]]
```

```{r}
list("John", 42, 
  list("Mary", 35,
    c(1, 22, 53))
  )[[3]][[3]][[2]]
```

take out 22

  * [[3]] extract 
  
```{r}
list("Mary", 35,
    c(1, 22, 53))[[3]]
```

  * [[3]] extract

```{r}
c(1, 22, 53)[[2]]
```

  * [[2]] extract
  
```{r}
22
```



```{r}
list(
  "John", 
  42, 
  list(
    "Mary", 
    35,
    c(
      1, 
      22, 
      53))
  )

```


## 2.10

```{r}
list("a", list(1, 2), TRUE)
```


```{r}
c(c("a", "b"), "c")
```
"a" "b" "c"
```{r}
c("a", "b", "c")
```

```{r}
c(c("a", "b"), c("c", "d"))
```

  * "a" "b" "c" "d"
  
```{r}
c("a", "b", "c", "d")
```
```{r}
c(c("a", "b"), c("c", "d"))
```

extract "d"

```{r}
c(c("a", "b"), c("c", "d"))[[2]][[2]]
```
```{r}
c("a", "b", "c", "d")[[4]]
```

```{r}
list(c("a", "b"), c("c", "d"))[[2]][[2]]
```

list respects element values structure

c however will break down vector if it sees one.

```{r}
c(list("a", 1), list("c", 2))
```

  * "a", 1, "c", 2


```{r}
c("a", 1, "c", 2)
```
Coercion
1
3
2
```{r}
1 + 2
"1" +2
'Martin' + 2
```

## 2.12

Four features

  * age, gender, residence, income

### Obo

(1) 54 male north 100

```{r}
age = 54
gender = "male"
residence = "north"
incomes = 100
```

```{r}
A <- list(54,"male","north",100)
```

(2) 32 female south 25


```{r}
age = 54
gender = "male"
residence = "north"
incomes = 100

age = 32
gender = "female"
residence = "south"
incomes = 25
```

```{r}
A <- list(54,"male","north",100)
B <- list(32, "female", "south", 25)
C <- list(28, "female", "east", NA)
D <- list(20, "male", "east", 77)
```

  * Not Available


Data set 
```{r}
data_set <- list(A, B, C, D)
```

```{r}
data_set
```




Ex 2.2
 
 * list(54, ..., 100): 54, "male", "north, 100
 
 * list(32, ..., 25): 23, "female", ..."25

```{r}
c(
  list(54, "male", "north", 100), # (1)
  list(32, "female", "south", 25), # (2)
  list(28, "female", "east", NA), # (3)
  list(20, "male", "east", 77) # (4)
)
```

(程式測試，請忽略)
```{r}
list(54, "male", "north", 100, 
  32, "female", "south", 25,
  28, "female", "east", NA, 
  20, "male", "east", 77) 
```



### Misc


```{r}
54
male # name call. R will find what the name represents

```


```{r}
age = 54
gender = "male"
residence = "north"
incomes = 100
```

```{r}
gender <- "Male"
residence -> "north"
income -> 100
age -> 54
```

```{r}
gender <- "Male"
gender = "Male"
```

```{r}
gender -> "Male"
"Male" = gender
Male = gender
```



```{r}
gender # name call
gender = "male" # binding
gender <- "male" # binding
gender -> "Male"
```

```{r}
gender -> "Male"
```

I call the value of the name (gender) represents, and bind the value to the name called ("Male")
```{r}
"gender" -> "Male"
"gender" -> Male
Male = "gender"
```

Value always stay at the tail of an arrow

<- tail

tail -> 





