## Exercise 5.1 
Load the following data set:

```{r exercise5-1}
# Observation by observation
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)

```

Data set `concerts_obo` has difference performance information as its observations. For each performance, there can be more than one show, and each show's information is contained inside the observation's `showInfo` element. 

  1. How many shows does the 5th performance have?

```{r, echo=FALSE}
concerts_obo[[5]]$showInfo |> length()
```
 
  2. If we are to find out the number of shows **for each** performance, what is the **.x-pattern**?

```{r, echo=FALSE}
# Assume number_of_shows object exists
number_of_shows[[.x]] <- concerts_obo[[.x]]$showInfo |> length()
```
  
  3. Find out the number of shows **for each** performance, and put the answer as an integer vector under `analysis$number_of_shows`. (i.e. `analysis$number_of_shows[[5]]` will show your answer in 1.)
  
```{r, echo=FALSE}
number_of_shows <- vector("integer", length(concerts_obo))
for(.x in seq_along(concerts_obo)){
  number_of_shows[[.x]] <- concerts_obo[[.x]]$showInfo |> length()
}

print(number_of_shows)
```

  4. Construct a data frame with columns, **title**, **date**, **location** and **locationName**, where **title** comes from each observation's title, and the rest three are from each observation's 1st showInfo. In addition, **date** column has to be "POSIXct" "POSIXt" class with Taipei time zone.
  
```{r, echo=F}
number_of_concerts <- length(concerts_obo)
.titles <- .dates <- .locations <- .locationNames <- character(number_of_concerts)
for(.x in seq_along(concerts_obo)){
  .titles[[.x]] <- concerts_obo[[.x]]$title
  .dates[[.x]] <- concerts_obo[[.x]][["showInfo"]][[1]][["time"]]
  .locations[[.x]] <- concerts_obo[[.x]][["showInfo"]][[1]][["location"]]
  .locationNames[[.x]] <- concerts_obo[[.x]][["showInfo"]][[1]][["locationName"]]
}

latestShow <- data.frame(
  title=.titles,
  date=.dates |> lubridate::ymd_hms(tz="Asia/Taipei"),
  locationName=.locationNames,
  location=.locations
  )
View(latestShow)
```

  * `if(pick5_1_4[[.x]]==T){` can be reduced to `if(pick5_1_4[[.x]]){` since `pick5_1_4[[.x]]` is already logical.
  * When the same `iterate generation` happens several time, try to combine the .x-patterns. 
   <https://github.com/AmyChen20021003/110-1-r4ds-main/blob/fdca3bce1bf5fbe8fdad6f52abe8ac7cc6ff3dd8/5-1.Rmd#L32>

## Ex 5.2
Regarding the `drug` data from Exercise 4.8. 
```{r exercise5-2, echo=F}
drug <- list()
drug$source[[1]] <- 
  "https://docs.google.com/spreadsheets/d/17ID43N3zeXqCvbUrc_MbpgE6dH7BjLm8BHv8DUcpZZ4/edit?usp=sharing"
drug$data <- 
  googlesheets4::read_sheet(
    drug$source[[1]]
  )
```

```{r, echo=F}
drug$data |> View()
.df <- drug$data
names(.df) <- .df[1, ] |> unlist()
.df <- .df[-1, ]
names(.df)[5:7] |> teachDS::writeObject2Clip(T)
.df[c('發生場所一','發生場所二','發生場所三')] |> unlist() |> table() |> View()
.df$發生場所一 |> table() |> View()
```

  1. For each kind of drug (`毒品品項`), what was the average amount of drug (the mean of `數量（淨重）_克`) found?

```{r, echo=F}
.df <- drug$data

# fixed column names
names(.df) <- .df[1, ] |> unlist()
.df <- .df[-1, ]

.df$`數量（淨重）_克` |>
  as.numeric() -> .df$`數量（淨重）_克`
.df |> split(.df$毒品品項) -> grouped_dfs
averageAmounts <- vector("double", length(grouped_dfs))
for(.x in seq_along(grouped_dfs)){
  averageAmounts[[.x]] <- 
    mean(grouped_dfs[[.x]]$`數量（淨重）_克`, na.rm=T)
}
names(averageAmounts) <- names(grouped_dfs)
View(averageAmounts)
```

  2. Add a column `date` to the data frame which is a date class created from the column `發生日期`

```{r, echo=F}
.df$date <- {
  .df$發生日期 |>
    as.integer() -> .minguoDates
  lubridate::ymd(.minguoDates + 19110000)
}
```


For the following question, we only consider those `毒品品項` that contains the words "安非他命".

```{r, echo=FALSE}
pick <- .df$毒品品項 |> stringr::str_detect("安非他命")
subsample <- .df[pick, ]

```

  3. For each year, what was the total amount found? (Apply `lubridate::year()` to `date` column will get you year)

```{r, echo=FALSE}
subsample$date |> lubridate::year() -> years
subsample |> split(years) -> subsample_byYear
amount <- vector("double", length(subsample_byYear))
for(.x in seq_along(subsample_byYear)){
  amount[[.x]] <- sum(subsample_byYear[[.x]]$`數量（淨重）_克`, na.rm=T)
}
ans3 <- data.frame(
  year=names(subsample_byYear),
  amount=amount
)
View(ans3)
```

## Ex5.3

 It is very common that economic model has some equilibrium condition as the intersection of two straight lines, like demand and supply. They can be expressed as:
demand: p_d(q)=a+bq
supply: p_s(q)=c+dq
In equilibrium,
```
(p*, q*) satisfies p_d(q*)=p_s(q*) and p*=p_d(q*)=p_s(q*).
```

If you solve for $q*$ and $p*$,
```
q*=(a-c)/(d-b)
p*=a+bq*.
```
1. Run the following code and solve for equilibrium and save it in a list with two element names q_star and p_star. Each has its value in corresponding to q* and p* that your program solved.
```{r}
a=1; b=-3; c=0; d=1
```

```{r, echo=FALSE}
q_star <- (a-c)/(d-b)
p_star <- a+b*q_star
equilibrium <- list("q_star"=q_star, "p_star"=p_star)
equilibrium
```


  * An error: 
  
```{r}
a=1; b=-3; c=0; d=1
# 1
pick5_3_1=list(
  q_star=(a-c)/(d-b), 
  p_star=a+b*q_star
)
pick5_3_1
```


2. Create a function called solve_equilibrium so that the following code would work:
```{r}
a=1; b=-3; c=0; d=1
equilibrium1 <- solve_equilibrium()
print(equilibrium1)

a=2; b=-3; c=0; d=1
equilibrium2 <- solve_equilibrium()
print(equilibrium2)

a=1; b=-3; c=0; d=1.5
equilibrium3 <- solve_equilibrium()
print(equilibrium3)
```

```{r, echo=FALSE}
solve_equilibrium <- function(){
  q_star <- (a-c)/(d-b)
  p_star <- a+b*q_star
  equilibrium <- list("q_star"=q_star, "p_star"=p_star)
  equilibrium
}

a=1; b=-3; c=0; d=1
equilibrium1 <- solve_equilibrium()
print(equilibrium1)

a=2; b=-3; c=0; d=1
equilibrium2 <- solve_equilibrium()
print(equilibrium2)

a=1; b=-3; c=0; d=1.5
equilibrium3 <- solve_equilibrium()
print(equilibrium3)
```


