
# Exercise 4.1 Parse customerExperience into an ordered factor atomic vector:

  * ordered: can compare magnitude of different responses. `factor(..., ordered= T)`
  
  * factor: `factor()`

```{r}
customerExperience <- c('very happy','very happy','satisfied','satisfied','satisfied','very happy','bad','bad','satisfied','satisfied','bad','happy','happy','very happy','happy','happy','satisfied','very happy','very happy','satisfied','satisfied','very happy','satisfied','bad','very happy','very bad','very happy','bad','bad','very bad')
customerExperience_fct_ordered <- 
  factor(
    customerExperience, 
    levels = c('very happy','happy','satisfied','bad','very bad'),
    ordered = T
  )

customerExperience_fct_ordered <- 
  factor(
    customerExperience, 
    levels = c('very bad','bad','satisfied','happy','very happy'),
    ordered = T
  )

customerExperience_fct_ordered[[1]] > 'bad' # "very happy" > 'bad'

table(customerExperience_fct_ordered)
```

## exercise 4.2

```{r}
subsidiaries <- list() # declare
subsidiaries$boston <- c("2020 Oct. 13 15:00:00", "2019 Apr. 10 09:30:00") # boston time zone
subsidiaries$mykonos <- c("14 Jan., 2021 03:27:00", "8 Aug., 2020 11:20:00") # mykonos time zone
```

Parsing a date/time character vector without tz setting can yield wrong result.

Also make sure you choose the right tzone expression. 
```{r}
subsidiaries <- list()
subsidiaries$boston <- lubridate::ymd_hms(c("2020 Oct. 13 15:00:00", "2019 Apr. 10 09:30:00"),
  tz="America/New_York")# boston time zone
subsidiaries$mykonos <- lubridate::dmy_hms(c("14 Jan., 2021 03:27:00", "8 Aug., 2020 11:20:00"),
  tz="Europe/Athens") # mykonos time zone
```


```{r}
lubridate::with_tz(
  c(
    subsidiaries$boston,
    subsidiaries$mykonos
  ),
  tz="Asia/Calcutta"
)
```

## exercise 4.3

```{r}
dfExercise <- list()
dataSet1 <- list(
  name=c("John", "Mary", "Ben"),
  age=c(33, 45, NA)
)
# 2
dfExercise$data1 <-
  data.frame(
    dataSet1
  )

# 3

dataSet1$children[[1]] <- list(
  list(name="Jane", age=2))
dataSet1$children[[2]] <- list(
  list(name="Bill", age=3),
  list(name="Ken", age=0))
dataSet1$children[[3]] <- list(
  list(name="William", age=10))

# 4
dfExercise$data2 <- list2DF(dataSet1)
```


**Declare-and-add** method on **list** when creating a nested list using multiple chained-retrievals, there is a rule to remember:

  * If `[[]]` is used, then it must be at the last. 

```{r}
l0 <- list() # declare
l0[[1]]$name <- "John" # won't work
l0$name[[1]] <- "John" # work
```
  
```{r}
l0$secondPerson$name <- "Jane" # work
l0$secondPerson$children[[1]] <- "Albigail" # work
l0$secondPerson[[3]]$habit <- "tennis" # won't work
```



