How do you sum the following Chinese numbers? 
```{r}
c('參','貮','貮','貮','壹','貮','參','貮','參','參')
```

```{r}
fct <- factor(
  c('參','貮','貮','貮','壹','貮','參','貮','參','參'),
  levels=c('壹','貮','參')
)
sum(as.numeric(fct))
```

## 4.7

The following is 5 to 9 in Persian language:

```{r}
persian5to9 <- c("۵", "۶", "۷", "۸", "۹")

```

How do you sum the following Persian numbers?
```{r}
persian0 <- c('۶','۹','۸','۹','۶','۸','۸','۵','۹','۹')

```

```{r}
persian5to9_map2_5to9 <- 5:9
fct_persian0 <- factor(
  persian0, 
  levels=persian5to9
)
persianMap2_5to9Position <- 
  as.numeric(fct_persian0)
sum(persian5to9_map2_5to9[persianMap2_5to9Position])
```

# 4.8

A school adopt letter grade system from C to A+ as follows:

```{r}
letter_grades <- c("C", "B-", "B", "B+", "A-", "A", "A+")
```

However, when there is need to calulate GPA, they convert each letter grade to each value in the following numeric_grades vector:

```{r}
numeric_grades <- c(2, 2.5, 3, 3.5, 4, 4.5, 5)
```


A student with the following letter grades need to convert them to numeric_grades:

```{r}
studentGrades <- c('B','A','A+','B+','A-','B','B-','B','A+','B+','C','B-','B-','B','C','C','B+','B','B+','B')
```


He asked you for help. You layout the following programming plan:

```{r}
studentLetterGrades <- {
  # Task map c("C", "B-", "B", "B+", "A-", "A", "A+") to c(2, 2.5, 3, 3.5, 4, 4.5, 5)
  
  # step1: for each grade in studentGrades find its position in c("C", "B-", "B", "B+", "A-", "A", "A+") so if studentGrades = c("C","A-"), step1 = c(1, 5) since c("C", "B-", "B", "B+", "A-", "A", "A+")[c(1, 5)] will give him "C", "A-"
  
  # step2: Use step1 result as position indices to retrieve from c(2, 2.5, 3, 3.5, 4, 4.5, 5). From previous example, step1=c(1, 5), then  c(2, 2.5, 3, 3.5, 4, 4.5, 5)[step1] will give him c(2, 4)
  
}
```

Complete the programming block.
