

```{r}
typeof(c("John", "Mary"))
typeof(c(2, 3.1412))
typeof(c(TRUE, TRUE, F))
```


```{r}
class(c("John", "Mary"))
class(c(2, 3.1412))
class(c(TRUE, TRUE, F))
```

**class** is a categorisation method that categorises different values based on **what we can do with those values**.

  
  * type: man and woman
  
  * class: difference based on skills. (plumber class, teacher class)
  
***

```{r}
# date time information
dateTimeInfo <- "2021-01-01 12:03:33"
typeof(dateTimeInfo)
```


```{r}
class(dateTimeInfo)
```

```{r}
dateTimeInfo + 20
# character class value + 20
```

 we can choose proper parsing function to teach R understand a date time value is more than a character--teach R understand a class called date/time.
 
```{r}
dateTimeInfo2 <- lubridate::ymd_hms("2021-01-01 12:03:33")
class(dateTimeInfo2)
```

  * lubridate::ymd_hms is a parsing function to teach R understand date time. 
 
```{r}
dateTimeInfo2 + lubridate::seconds(20)
```

type: how we store **raw** information

class: what we (R) can do with different informations















