# 4.13

```{r}
johnDoe <- list()
johnDoe$source[[1]] <- "https://www.moj.gov.tw/2204/2771/2773/76135/post"
johnDoe$source[[2]] <- "https://docs.google.com/spreadsheets/d/1g2AMop133lCAsmdPhsH3lA-tjiY5fkGIqXqwdknwEVk/edit?usp=sharing"
googlesheets4::read_sheet(
  johnDoe$source[[2]]
) -> johnDoe$data
```

1.For those whose reported unit (通報機構) is not NA, what are their records? (in other words, construct a reported-unit-not-NA subsample)

2.For those dead bodies reported (通報機構) by “海巡隊” (use =="海巡隊" here. Ignore other similar unit names), what are their death types (死亡方式描述)? How many bodies in each type?

3.For those whose death type (死亡方式描述) is 不詳 or 他殺, what are their discovered counties (發現縣市)? How many such bodies in each counties?

```{r}
# 1
pick13_1 <- !is.na(johnDoe$data$通報機關名稱)
johnDoe$data[pick13_1, ] -> subsample
View(subsample)
# 2
pick13_2 <- johnDoe$data$通報機關名稱 == "海巡隊"
johnDoe$data$死亡方式描述[which(pick13_2)]
## use which(pick) will ignore those NA in pick. Nice trick 
table(johnDoe$data$死亡方式描述[which(pick13_2)])
# 3
pick13_3 <- johnDoe$data$死亡方式描述 == "不詳" | johnDoe$data$死亡方式描述 == "他殺"
johnDoe$data$發現縣市 [which(pick13_3)]
table(johnDoe$data$發現縣市 [which(pick13_3)])
```

  * `pick` will keep NA. `which(pick)` will not.
  
```{r}
# This is okay as well
pick13_3 <- johnDoe$data$死亡方式描述 %in% c("不詳", "他殺")

# This is not okay.
pick3<-johnDoe[["data"]][["死亡方式描述"]]==c("不詳","他殺")
country<-johnDoe[["data"]][["發現縣市"]][pick3]
table(country)

```

## Exercise 4.14 

Get fraud$data from exercise 3 in Exercise section. The following questions exclude any NA.

1. Convert 通報日期 to a date class. Is there any NA after conversion?

2. How many LINE accounts were reported as a fraud after 2018 (i.e. starting from 2019-01-01)?

3. How many LINE accounts were reported as a fraud between year 2019 and 2020?


```{r}
fraud <- list()
fraud$source[[1]] <- "https://data.gov.tw/dataset/78432"
fraud$source[[2]] <- "https://data.moi.gov.tw/MoiOD/System/DownloadFile.aspx?DATA=7F6BE616-8CE6-449E-8620-5F627C22AA0D"
fraud$data <- readr::read_csv(fraud$source[[2]])
```


```{r}
# 1
fraud$data$通報日期 |> class()
fraud$data$通報日期 |>
  lubridate::ymd() -> fraud$data$通報日期
any(is.na(fraud$data$通報日期))
# 2
pick14_2 <- fraud$data$通報日期 >= lubridate::ymd("2019-01-01")
sum(pick14_2, na.rm = T)
# 3
pick14_3 <- fraud$data$通報日期 >= lubridate::ymd("2019-01-01") & fraud$data$通報日期 < lubridate::ymd("2021-01-01")
sum(pick14_3, na.rm = T)
```

  * If the class of `fraud$data$通報日期` is character, 
  `fraud$data$通報日期 >= lubridate::ymd("2019-01-01")` will convert `fraud$data$通報日期` on the run for you implicitly.
