---
title: "110-1-r4ds Midterm"
params:
  name: "林木木"
  id: "411073221"
---

**Please change 林木木 to your name, and 411073221 to your school id.**

**All program lines must be inside a corresponding code chunk, like the one below.**


```{r}

```

# Econ Survey

An online survey is distributed to students of Economics department. There are two questions:

  * question 1: Are you happy with our campus? Choose a number from 5(very happy), 4(happy), 3(satisfy), 2( unhappy), to 1(very unhappy). 
  
  * question 2: Did you participate in any of the following activities? Check all that apply to you. (student association, school club, school sport team, department sport team)

Other than those two questions, the survey system record also the following information:

  * name  (a character)
  * grade  (an integer from 1 to 4)
  
To collect survey information, we have to design what data structure to use for each submission (aka each observation).

***

For one submission from freshman Mary, whose response to question 1 is 5, to question 2 is student association and department sport team. Consider the following list structure to recorde this observation:

  * name: "Mary"
  * grade: 1
  * responses: 
     1. 5
     2. c("student association", "department sport team")

Based on the list, we want the following retrievals can get a value shown after # sign.
```{r}
observation$name # "Mary"
observation$grade # 1
observation$responses[[1]] # 5
observation$responses[[2]] # c("student association", "department sport team")
```

Construct a list and bind it with name observation so that the above retrievals deliver the results shown after # sign

```{r}
observation <- list()
observation$name <- "Mary"
observation$grade <- 1
observation$responses[[1]] <- 5
observation$responses[[2]] <- list("student association", "department sport team")
```


```{r}
observation2 <- observation
observation2$name="John"
observation2$grade=3
observation2$responses[[1]]=4
observation2$responses[[2]]=c("school club")
unlist(observation2)

unlist(observation) -> obs_unlist
obs_unlist
relist(obs_unlist, observation2)
```



